### 2017-01-11 robust-software.tex
Removed authentication sentence for #33; added web service mention for #31

Unfortunately, reusing software (whether software libraries or separate executables)
introduces dependencies, which can
bring their own special pain. The interface between two software
packages can be a source of considerable frustration: all too
often, support requests descend into debugging errors produced by the
other project due to incompatible libraries, versions, or operating
systems~\cite{brown2013}. Even introducing libraries in the same programming
language can rely on software installed in the environment.

@@

First, 
\textbf{make sure that you really need the auxiliary program}. If you are
executing GNU sort instead of figuring out how to sort lists in Python,
it may not be worth the pain of integration. Reuse software that offers some
measurable improvement to your build environment.

Second, if launching an executable, \textbf{ensure the appropriate software and version is available}.
Either allow the user to
configure the exact path to the package, distribute the program with the
dependent software, or download it during installation using your
package manager.

Third, \textbf{ensure that reused software is robust}. Relying on erratic third
party libraries or software is a recipe for tears. Prefer software that follows
good software development practices, is open for support questions, and is
available from a stable repository using your package manager.

@@

\item[\textbf{Services}] The rules we present above are necessary, but
  not sufficient, for software that needs to interact with services
  such as database and web servers.  Such software is often stopped
  and started under automatic control, may need to authenticate, etc.,
  all of which are out of scope of this paper.

>>>>

Unfortunately, reusing software (whether software libraries or separate executables)
introduces dependencies, which can
bring their own special pain. The interface between two software
packages can be a source of considerable frustration: all too
often, support requests descend into debugging errors produced by the
other project due to incompatible libraries, versions, or operating
systems~\cite{brown2013}. Even introducing libraries in the same programming
language can rely on software installed in the environment, and the problem
becomes much more difficult when relying on executables, or even on web
services.

@@

First, 
\textbf{make sure that you really need the auxiliary program}. If you are
executing GNU sort instead of figuring out how to sort lists in Python,
it may not be worth the pain of integration. Reuse software that offers some
measurable improvement to your project.

Second, if launching an executable, \textbf{ensure the appropriate software and version is available}.
Either allow the user to
configure the exact path to the package, distribute the program with the
dependent software, or download it during installation using your
package manager. If the executable requires internet access, check for that
early in execution.

Third, \textbf{ensure that reused software is robust}. Relying on erratic third
party libraries or software is a recipe for tears. Prefer software that follows
good software development practices, is open for support questions, and is
available from a stable location or repository using your package manager.

@@

\item[\textbf{Services}] The rules we present above are necessary, but
  not sufficient, for software that needs to interact with services
  such as databases and web servers, or coordinates multiple hosts or interfaces, 
  and is out of scope of this paper.
